Block bootstrap consistency\\under weak assumptions

### 2016-06-17 Paper.tex
[#20] Tweak notation for centered bootstrap BM
The referee suggested using \bar{\mu}^*_n instead of using no bar.
This commit makes the change.
[#27] Tweak wording in paper

The assumption on the dispersion of the individual means,
$(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
\citepos{GoJ:03} when the expected block length is $o(\sqrt{n})$. When
the blocks are longer than $o(\sqrt{n})$, a case that \citet{GoW:02}
and \citet{GoJ:03} do not consider, the dispersion must be smaller.
To see these implications of this assumption, it is helpful to
consider a simple example: a stochastic process with a single break of
size $\Delta_n$ at time $T_n$,
\begin{equation*}
\mu_{nt} =
\begin{cases}
  \mu & \text{if } t \leq T_n \\
  \mu + \Delta_n & \text{otherwise}
\end{cases}
\end{equation*}
A small amount of algebra gives the relationship,
\begin{equation*}
  \sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  = T_n (n - T_n) \Delta_n^2 / n \equiv D_n;
\end{equation*}
we have defined $D_n$ to minimize notation in the subsequent
discussion.  For the Moving and Circular Block Bootstraps,
Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
the Stationary Bootstrap the same relationship must hold for the
expected block length. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
some constants $\Delta_0$ and $\pi$ and for all $n$, then
$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
there is a break large enough that its timing could be precisely
estimated \citep[as in][]{Bai:94}, but the break is ignored and the
bootstrap is applied to the entire dataset.

We can also use the same DGP to produce scenarios where
Theorem~\ref{T1}'s Assumption~2 is satisfied.  The first mimics a
setting where the break is estimated and the bootstrap is applied to
the post-break sample, but a small number of pre-break observations
are accidentally included in the data set as well. Here
$\Delta_n = \Delta_0$ and $T_n = T_0$ for some finite $T_0$. In this
case, Assumption 2 holds hold as long as $M_n = o(\sqrt{n})$.
Similarly, if the break is moderate with unknown timing in the sense
of \citet{ElM:07}, so $\Delta_n = \Delta / \sqrt{n}$ and
$T_n = \pi n$, then $D_n \approx \Delta c (1 - c)$ and Assumption 2
again holds as long as $M_n = o(\sqrt{n})$. Consequently, block sizes
of length $o(\sqrt{n})$ ensure that the conditions of
Theorem~\ref{T1}'s when there is a moderate amount of
heterogeneity---either because the sample is chosen to lie after a
large break estimated break or because any breaks are smaller in
magnitude and, consequently, potentially difficult to detect. When the
degree of heterogeneity is very small or nonexistent, so
$\sum_t (\mu_{nt} - \bar \mu_n)^2$ grows even slower, then larger
block lengths can also satisfy Assumption 2.

@@

Theorem~\ref{T1} can also be extended to give an \fclt\
using arguments from \citet{JoD:00b}. We show in
Theorem~\ref{T2} that the partial sum
of the bootstrapped process obeys an \fclt\ and can be used to derive
critical values for other test statistics under the same assumptions
as Theorem~\ref{T1}. For this result, define the
following partial sums,
\begin{align*}
W_n(\gamma) &=
\tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma n \rfloor}
(X_{nt} - \bar\mu_n) &&\text{and}&
W_n^{*}(\gamma) &= \tfrac{1}{\sqrt{n}}
\sum_{t=1}^{\lfloor \gamma n \rfloor}
(X^*_{nt} - \mu_n^{*}).
\end{align*}
Also let $W$ denote standard Brownian Motion and $\sigma W$ denote
Brownian Motion scaled by the constant $\sigma$.

>>>>

The assumption on the dispersion of the individual means,
$(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
\citepos{GoJ:03} under their additional requirement that the
expected block length be $o(\sqrt{n})$. When
the blocks are larger than $o(\sqrt{n})$, a case that \citet{GoW:02}
and \citet{GoJ:03} do not consider, the dispersion must be smaller.
To see these implications of this assumption, it is helpful to
consider a simple example: a stochastic process with a single break of
size $\Delta_n$ at time $T_n$, implying
\begin{equation*}
\mu_{nt} =
\begin{cases}
  \mu & \text{if } t \leq T_n \\
  \mu + \Delta_n & \text{otherwise}
\end{cases}
\end{equation*}
A small amount of algebra gives the relationship,
\begin{equation*}
  \sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  = T_n (n - T_n) \Delta_n^2 / n \equiv D_n;
\end{equation*}
we have defined $D_n$ to minimize notation in the subsequent
discussion.  For the Moving and Circular Block Bootstraps,
Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
the Stationary Bootstrap the same relationship must hold for the
expected block length. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
some constants $\Delta_0$ and $\pi$ and for all $n$, then
$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
there is a break large enough that its timing could be precisely
estimated \citep[as in][]{Bai:94}, but the break is ignored and the
bootstrap is applied to the entire dataset.

We can also use the same DGP to produce scenarios where
Theorem~\ref{T1}'s Assumption~2 is satisfied.  The first mimics a
setting where the break is estimated and the bootstrap is applied to
the post-break sample, but a small number of pre-break observations
are accidentally included in the data set as well. Here
$\Delta_n = \Delta_0$ and $T_n = T_0$ for some finite $T_0$. In this
case, Assumption 2 holds hold as long as $M_n = o(\sqrt{n})$.
Similarly, if the break is moderate with unknown timing in the sense
of \citet{ElM:07}, so $\Delta_n = \Delta / \sqrt{n}$ and
$T_n = \pi n$, then $D_n \approx \Delta c (1 - c)$ and Assumption 2
again holds as long as $M_n = o(\sqrt{n})$. Consequently, using block sizes
of length $o(\sqrt{n})$ ensures that Theorem 1's assumptions on the
dispersion of the $\mu_{nt}$ hold when there is a moderate amount of
heterogeneity---either because the sample is chosen to lie after a
large break estimated break or because any breaks are smaller in
magnitude and, consequently, potentially difficult to detect. When the
degree of heterogeneity is very small or nonexistent, so
$\sum_t (\mu_{nt} - \bar \mu_n)^2$ grows even slower, then larger
block lengths can also satisfy this condition.

@@

Theorem~\ref{T1} can also be extended to give an \fclt\
using arguments from \citet{JoD:00b}. We show in
Theorem~\ref{T2} that the partial sum
of the bootstrapped process obeys an \fclt\ and can be used to derive
critical values for other test statistics under the same assumptions
as Theorem~\ref{T1}. For this result, define the
following partial sums,
\begin{align*}
W_n(\gamma) &=
\tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma n \rfloor}
(X_{nt} - \bar\mu_n) &&\text{and}&
W_n^{*}(\gamma) &= \tfrac{1}{\sqrt{n}}
\sum_{t=1}^{\lfloor \gamma n \rfloor}
(X^*_{nt} - \bar\mu_n^{*}).
\end{align*}
Also let $W$ denote standard Brownian Motion and $\sigma W$ denote
Brownian Motion scaled by the constant $\sigma$.
